\section{Arduino Architecture}

The robot is controlled by an on-board Arduino unit. This is programmed to
receive input from a native RF module, as well as the wheels' rotary encoders.
Further, it controls the four movement motors, the single grabber motor, and
the power flow to the solenoid kicker. The Arduino main loop does three
things: It checks for new commands received via RF, it updates the rotary
encoder positions with the latest reading, and it updates its internal state
and, if necessary, adjusts the motor outputs. This is repeated until the
Arduino is turned off.

\subsection{Low-Level Commands}

Internally, the Arduino operates using a set of low-level commands, which are
similar but separate from the communications ABI. Examples of such commands
include opening the grabbers for a set amount of time, or moving to the right a
specified distance. Each command is a sequence of one or more bytes, the first
of which always identifies the command. The most significant bit of the first
byte indicates the interruptibility of the command, which will be discussed
later, with one indicating uninterruptibility, and zero indicating
interruptibility. The remaining 7 bits indicate the command itself, the
different possible values and their meaning are tabulated in \cref{llcmd}. As
with the communications ABI, depending on the command, a set number of argument
bytes will follow.

Low-level commands correspond directly to a single action the robot should
currently be doing, differing in this from the communications ABI, in which a
single command may specify a sequence of actions. For example, the
communications `\texttt{KICK}' command describes a sequence of grabber
movements and solenoid actuation, each part of which is an individual low-level
command. Low-level commands typically have clearly defined Arduino outputs
(spinning the grabber motors, and enabling the solenoid in the previous
examples), as well as clear completion criteria, such as time elapsed or
distance travelled. Once a command is completed, the Arduino commences the next
low-level command immediately.

\subsection{Comms Input}

If the RFs internal buffer contains a valid sequence of new instructions (see
\cref{comms}), this is translated into more low-level instructions which can be
used by the Arduino directly, and the buffer is cleared. If the RFs internal
buffer is \textit{not} a valid sequence of new instructions, but contains a new
line, it is considered to be a malformed packet, and the buffer is also
cleared.

The translation to low-level commands occurs immediately upon receiving new
instructions, and involves mapping each of the ABI commands to one or more
low-level commands. For more detail of what low-level commands are generated
for each ABI command, see \cref{abi}. The new string of low-level commands
effectively replace any in the current buffer, with a few notable exceptions.
Some commands (e.g. kicking or the grabbers opening), are uninterruptible,
and cannot be replaced once they have been commenced. Since these also compile
down into a sequence of low-level commands, this sequence should not be
interrupted. This is achieved with the `uninterruptible' flag bit. If the first
low-level command is uninterruptible, the newly to insert commands do not
replace it, but instead the first interruptible command in the list. In order
to allow two sequences of uninterruptible commands to be treated as separate,
an interruptible \texttt{NOP} is inserted after each sequence of
uninterruptible commands.

\subsection{Distance}

For multiple of the low-level commands, the distance the robot has travelled,
or the angle it has rotated needs to be known. This is calculated from the
values taken off the rotary encoders on each wheel, which indicate how far
these wheels have rotated. In practice, due to the inconsistencies such as the
wheels not stopping immediately and turning at differing powers, these values
are not completely linear with the distance travelled or the angle rotated.
Instead, a non-linear approximation function was created from measured values
to translate rotary encoder positions into workable values for the distance
travelled or the angle rotated. This function uses measured values for several
points, behaving linearly between them.

\subsection{Auto-Correction}

Due to the motors on different sides having different powers, and asymmetry in
the design, without any corrections the robot drifts to one side. To compensate
for this, the motor powers are updated every time the main loop is run, and
motors whose rotary encoders show that they are ahead of the rest are
throttled. In practice, this approach introduces a slight jerkiness and
unpredictability to the movement, however it improved overall reliability
significantly.
