\section{Architectural Overview}

The core control of the robot was split across an external PC and the onboard
Arduino Xino RF unit. An analog video feed with a top-down perspective of the
pitch was supplied to the external PC. The external PC is able to communicate
with the Arduino via a supplied radio frequency link. The PC uses a USB RF
device, while the Arduino has an inbuilt RF transmitter and receiver.

The external PC is responsible for all decision making, while the Arduino
carries out instructions passed to it quickly and accurately.
To begin with, the PC listens for new frames from the video input, and
processes these to extract a set of coordinates for objects of interest: The
robots (which are detected by their coloured top-plates), and the ball. This is
used to update in internal model of the world. A few adjustments are made to
smooth over misdetections by the vision system and correct positions to account
for the fact that the robot top-plates are elevated.

At set intervals, the planning module runs, taking a snapshot of the current
world state. It then determines what course of action to take in the current
situation, and what concrete instructions should be sent to the robot. These
instructions are then encoded into the instruction ABI, and transmitted via the
RF link. Finally, the Arduino receives the instructions and sets the power
outputs to the motors and the kicker accordingly. Some amount of feedback from
the rotary encoders on the motors allows the Arduino to adjust the motor powers
on the fly, to correct its movement. The Arduino determines by itself when an
instruction is over, and proceeds with the next one, or, if no instructions are
left, remains idle.

\subsection{Interaction of PC Components}

Since the controlling PC runs the vision, planning, and communications
components, their interaction is non-trivial. The entry point for the control
unit is a single main file, \texttt{main.py}, which accepts various parameters,
documented in \cref{params}. This first starts the vision subsystem in its own
thread, and registers a hook for receiving new world states. These world states
are generated by the vision, and then passed back to the main control unit,
which uses them to update its own, more detailed, world state. Instead of
immediately taking the values supplied by the vision, they are first
post-processed to ensure that the values received are sensible. For example, a
heuristic is used to filter out a detection of the ball several meters from its
last known position as sporadic (It should be noted, however, that this will
eventually switch to recognising the new position, should the ball remain
there, allowing actual sudden movements to automatically correct themselves).

The planning runs on a stop-and-go mechanism. The planner is run, which sends 
appropriate instructions to the robot. Then, the planner waits a specific
amount of time, which depends on the instructions it sent, and repeats. This
loop runs in a separate thread as well. A few notable exceptions are made for
this mechanism, with the planner being re-run immediately on certain
conditions. These include the ball being within range of the grabbers, and the
ball approaching our goal (to allow for timely blocking). Finally, the planner
requires human input for information about the game. In particular, it needs to
know whether the game is currently in normal play, waiting for a kickoff (and
by which team), waiting for a penalty shot (and by which team), or stopped. For
this purpose, a GUI is displayed to the operator, with buttons to select each
of these states. Upon starting, the game state is considered to be stopped.
