\newcommand\visiontodo[1]{\textbf{TODO: #1}}
% Disable todos
%\renewcommand\visiontodo[1]{}

\section{Vision}

The vision system was designed to be simple and fast, both to aid in
development and to minimise the delay of a movement on the pitch being
registered by the system. Originally a system was being developed from the
ground up, but after a number of failures and difficulties the decision was
made to use Group 12's working system. Group 12's system was adapted from a
previous year's system, and was used for the rest of the project.

\visiontodo{Find out which code Group 12's system was based on}

\subsection{Theory}

The task for the vision system is simple: to find and report of the position of
the robots (or more accurately, their coloured top plates) and the ball from an
overhead, colour image of the pitch. The design of our system addresses this as
follows. First coloured areas matching the colours of the ball and top plate
markers are identified in the image. These areas are then processed to
determine if they are the ball, part of a top plate, or random noise. For the
ball the size of the area is the deciding factor, and for top plate markers the
proximity of other areas of colours that would be expected for a top plate are
factored in. When an area of the image is identified as an area of interest
this area is reported. When a certain object is not found the system does not
report anything and this omission is handled in the main world model.

\subsection{Implementation}

The vision system is implemented as a Python module largely separate from the
rest of the system. It utilised the OpenCV library to process the overhead
camera feed, and preform the majority of processing. The vision system follows
a basic flow of information: the raw camera frame is retrieved, preprocessed,
and the information of interest is extracted. This information is passed to the
main module, before the vision system loops back to the start. After retrieval,
radial distortion is removed from the raw image. It is then blurred using a
Gaussian blur to reduce noise. This undistorted noise image is then converted
to the HSV (Hue Saturation Value) colour space before being passed to
information retrieval. The HSV colour space is used instead of the default BGR
(Blue Green Red) as the Hue component represents the colour largely independent
of brightness and intensity, allowing a particular colour (or colour range) to
be identified more accurate than could be using BGR.

From the HSV image, a binary image is produced for each of the colour ranges
used to identify objects (a red colour range for the ball, a pink one for the
pink top plate markers, etc.). This binary image is the same size as the HSV
image and is white when the pixels in the HSV value are in the colour range and
black elsewhere in the image.  Contours are then extracted from these binary
images and these contours are then preprocessed further to determine if they
are a ball or top plate marker.  Contours are vector representations of the
edges in an image, so in this case describe the shapes of the true areas in the
binary images. To determine if a red contour is the ball, the contour is first
checked to ensure it is not too small according to a configurable value. The
enclosing rectangle that has minimum area is then calculated. If this rectangle
has close to equal length side (within a certain threshold), the contour is
assumed to represent the ball. To find the top plate markers, the same process
is followed. The found markers are then grouped with those within close
proximity to the centre marker. The orientation of the top plate is calculate
by calculating the angle between the centre marker and the `odd one out' (the
outer marker of a different colour) which is then rotated 45\degree to give the
orientation of the front of the top plate.  After this information has been
extracted from the binary images, it is passed to the main module, and the
vision system continues with processing the next frame.

\visiontodo{High-level diagram showing flow of information through vision
    system}

\visiontodo{Appendix: screenshots for various stages of processing?}

\subsection{Problems}

The vision system, on average, performs well. There are, however, a number of
areas that could be improved. The objects are not always detected, often due to
the colour ranges being too narrow, although an increase would cause a large
number of misdetections. When the objects are detected, their positions often
jitter from one frame to another, due to noise in the camera images. The colour
based matching also introduces other problems such as the pink top plate
markers and red pieces of clothing being detected as the ball.
