\section{Usage}

Before use, ensure that the four lithium-ion batteries are fully charged. Our
group shares the charger with group 12. Ensure that the batteries are properly
inserted into the two battery holders at the rear of the robot. To turn on the
robot, flick the switch at the base of the battery packs. A red light will be
visible from the Arduino, indicating that it is powered.

Our robot is operated together with that of group 12, it is assumed that their
robot has also been switched on at this point. To begin with, the device paths
of both groups USB RF sticks must be determined. To determine these, first
insert the RF stick for group 11. Then run \texttt{ls /dev/ttyACM*} to list all
serial USB devices available. This should return only one path, which can be
noted as the path for group 11's RF stick. Group 12's device path can then be
determined by inserting their RF stick and re-running \texttt{ls /dev/ttyACM*}.
One new path should be among those returned, which can be noted as the path to
group 12's RF stick.

Further information required to run the control unit is: The room being played
in (3.D03 or 3.D04), which side of the pitch, left or right, is ours (viewed
from the door), and which color our team will have (blue or yellow). Armed with
this knowledge, make sure that a top plate of each colour, as well as the ball,
are on the pitch. Then, \texttt{cd} into the project root directory, and
execute the following command:

\shellcmd{./main -p game -1 <PATH1> -2 <PATH2> -c <COLOUR> --pitch <NUM> -g <SIDE>}

\noindent Using the following values for the arguments:

\begin{itemize}
    \item The path of group 11's RF stick for \texttt{<PATH1>}.
    \item The path of group 12's RF stick for \texttt{<PATH2>}.
    \item `\texttt{y}' or `\texttt{b}' for \texttt{<COLOUR>}, if our team is
        yellow or blue respectively.
    \item `\texttt{0}' or `\texttt{1}' for \texttt{<NUM>}, if the game is being
        played in room 3.D03 or 3.D04 respectively.
    \item `\texttt{left}' or `\texttt{right}' for \texttt{<SIDE>}, if our goal
        is on the left or the right side of the pitch respectively.
\end{itemize}

A few windows should open up, the most prominent one of which displays a still
of the pitch for calibration.

\subsection{Calibration}

On the still of the pitch all four top plates and the ball should be clearly
visible as positioned earlier. The terminal will prompt the operator to click
on samples of red, blue, yellow, green, and pink in turn, for the ball and the
top-plate parts of the respective colours. This calibrates for the colours,
ensuring that they are accurately detected. Of each colour, multiple samples
should be clicked, including all places it is visible on the pitch (i.e. the
green circles of all top plates, and not just one should be sampled). After
several samples of each colour have been clicked, press the `q' key to move on
to the next. The colours are queried in the order listed above, and a request
for samples of the current colour is also printed to the terminal. Once
calibrations are complete, they are saved locally. Due to changing light
conditions, you should recalibrate at least every few hours, however it is
possible to skip the calibration phase and use the saved values by pressing
escape at the start of calibration.

\subsection{Online Usage}

After the vision is lunched, there will be a window named \texttt{Filter}
output, where you can see the vision feed with objects drawn on it representing
the robots and the ball (if they are found).  Robots will be represented by an
inner circle for the team colour (yellow or blue), an outer circle identifying
which of the two team mates it is (pink or green, referring to the colour of
the majority of circles on the top plate) and an arrow giving the orientation
of the robot. The red ball is simply shown by drawing a red circle around it.
Further, two other windows will be open, containing several trackbars. These
trackbars are for filters that you can add to the output feed. There are
filters to show only specific colours, or to different effects to the frame.
For day to day usage, these do not need to be used.

While the control program is running, the overall strategy and logging can be
modified. Entering `\texttt{debug}', `\texttt{info}', `\texttt{warn}', or
`\texttt{error}', and pressing enter, sets the logging level appropriately.
Further, a window to select the game state will have opened, allowing selection
from `\texttt{kickoff-them}', `\texttt{kickoff-us}', `\texttt{penalty-them}',
`\texttt{penalty-us}', `\texttt{normal-play}', and `\texttt{stop}'. Pressing
any of these sets the game to the respective state. At startup, the state is
`\texttt{stop}', and the robots should remain idle. Once the referee orders a
kickoff, either `\texttt{kickoff-them}', or `\texttt{kickoff-us}' should be
pressed, depending on if the opposing team or our team has kickoff
respectively. Likewise, should the referee call for a penalty kick, either
`\texttt{penalty-them}' or `\texttt{penalty-us}' should be pressed, depending
on if the opposing team or our team take the penalty respectively. The
`\texttt{stop}' button can be pressed whenever the referee stops the game.
Although it should not have to be used typically, pressing
`\texttt{normal-play}' skips the kickoff phase of play, and immediately begins
playing. This may be useful if the program had to be restarted mid-match.

At halftime, both teams switch sides. The control program needs to be informed
of the switch, either by typing in `\texttt{switch}' into the console, and
pressing enter, or by closing the control program and re-running it with the
other pitch side. To terminate the control program, press `Ctrl-D' with the
terminal window selected. If this fails, press enter and try again.
